Iterative Imitation Learning with Reduced Human Supervision

### 2015-08-18 paper.tex
changed arm

In experiment, we had our human demonstrator provide one demonstration and then iterated both  DAgger and SHIV until the cost function was zero during the policy roll out. At each iteration, we sampled the pose of the target object from an isotropic Gaussian with a standard deviation that is equal to $5\%$ of the width of the table.

>>>>

In experiment, we had our human demonstrator provide one demonstration and then iterated both  DAgger and SHIV until the cost function was zero during the policy roll out. At each iteration, we sampled the pose of the target object from an isotropic Gaussian with a standard deviation that is equal to $3\%$ of the width of the table.
